<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Diffing R objects}
-->

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(objectdiff)
```

# Diffing Arbitrary R objects

The objectdiff package can be used to create a function that allows you to 
transform one object into another using a minimal amount of memory footprint.
This can be very useful when you're performing, for example, a lot of data
manipulation on data.frames in very small and modular steps and want
to be able to go back to a previous state. Consider the following example.

```{r}
iris2 <- iris
iris2[1, 1] <- 1
patch1 <- objectdiff(iris, iris2)
iris3 <- iris2
iris3[1, 1] <- 2
patch2 <- objectdiff(iris2, iris3)
```

The function `patch1` and `patch2` are closures that record the minimum amount
of information necessary to turn the original `iris` object into `iris2` and
then `iris3`. Instead of storing all three objects, which would be memory
prohibited (especially on larger data sets), we can instead store `iris`
along with its patches. This is a similar mechanism to many source control
systems like Git.

We can now restore `iris3` given that we have `iris`:

```{r}
print(identical(iris3, patch2(patch1(iris))))
```

The objectdiff function
---------

In general, any two R objects can be "diffed" against each other using
the `objectdiff` function that this package provides. Good performance 
will be obtained for atomic vectors, lists (including data.frame's),
and recursive combinations of these (e.g., very heterogeneous lists),
but for more complex transformations there may not be any gains. For example,
diffing a character vector against a function is non-sensical and will
produce a patch that completely forgets about the character vector and
simply produces the function.


```{r}
patch <- objectdiff(c(TRUE, FALSE), identity)
print(c(all.equal(patch(1), identity), all.equal(patch(iris), identity),
        all.equal(patch("basically anything becomes identity"), identity)))
```

In any case, a valid patch will always be produced that is guaranteed
to at least produce the same output object given the same input object
it was diffed with.

